Review: Redefining Domestication: Adaptive Introgression during Crop Expansion

### 2017-06-16 paper.tex
Update paper.tex

>>>>

\gmj{Li, are you familiar with the analytical tools MIGRATE-N and BAYESASS?  Rieseberg comapres these two to STRUCTURE at some length in the discussion of this paper:
https://biology.unm.edu/Whitney/Whitney%20Reprints/Scascitelli%20et%20al%202010.pdf
Should we include these two methods, even in passing, in this portion of the paper?}
